### 2016-12-01 ms/ms.tex
changed the abstract and the first paragraph of intro

\begin{abstract}  
  As the world continues to lose species at an alarming rate,
  anticipating a community's ability to resist collapse will depend on
  the strength of interaction networks. We know little, however, about
  how to re-assemble interacting communities through restoration, or
  the process of ecological network assembly more generally. Using an
  eight-year dataset comprising nearly $20,000$ pollinator visitation
  records, we explore the assembly of plant-pollinator communities at
  native plant restorations sites in an agricultural landscape. We
  find that species occupy highly dynamic network positions through
  time, causing the community assembly process to be punctuated by
  major network reorganizations. In contrast, the non-assembling
  networks do not restructure as frequently. The most persistent and
  generalized species are also the most variable in their network
  positions, contrary to what is expected by assembly following
  preferential attachment --- a widly supported assembly
  mechanism. Our results fundamentally alter our understanding of how
  communities assembly and how species interactions change through
  time while helping to inform efforts to re-assembly robust
  communities through restoration.
\end{abstract}

@@

%% introduce mutualisms, restoration, network assembly
When a species goes extinct, more than a species is lost. That species
interacted with other species in its community, likely in ways that
were important or even crucial to others' survival. When a community
--- a unique combination of interacting species --- loses one species,
the system becomes weaker. Global change has created a severe
biodiversity crisis, and as species are lost, so are their
interactions \citep{dunn2009sixth, barnosky2011has}. A community's
ability to resist collapse will depend on the strength of each
interaction network \citep{Memmott2004, Rezende2007, Bascompte2009,
  Thebault2010}. To safeguard ecological function, it has become
increasingly imperative to aid the recovery of lost interactions and
component biodiversity and by facilitating the assembly of robust
interaction networks via ecological restoration
\citep{menz-2010-4}. However, we know very little about how ecological
networks assemble in general, rendering restoration of interacting
communities quite difficult.

@@

Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[the ``rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}. An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

>>>>

\begin{abstract}

Species are being lost at an alarming rate and it is imperative to understand how communities assemble if we are to prevent their collapse or restore lost interactions. We know little, however, about how to re-assemble interacting communities through restoration, or the process of ecological network assembly more generally. Using an eight-year dataset comprising nearly $20,000$ pollinator visitation records, we explore the assembly of plant-pollinator communities at native plant restorations sites in an agricultural landscape. We find that species occupy highly dynamic network positions through time, causing the assembly process to be punctuated by major network reorganizations. The most persistent and generalized species are also the most variable in their network positions, contrary to what assembly through preferential attachment predicts. Our results fundamentally alter our understanding of how communities assembly and how species interactions change through time while helping to inform efforts to re-assemble robust communities through restoration. %It was re-assembly but I think it is re-assemble no?

\end{abstract}

@@

%% introduce mutualisms, restoration, network assembly
%When a species goes extinct, more than a species is lost. That species
%interacted with other species in its community, likely in ways that
%were important or even crucial to others' survival. When a community
%--- a unique combination of interacting species --- loses one species,
%the system becomes weaker. 
Species in ecological communities are linked through ecological interactions. Global change, however, has created a severe
biodiversity crisis, and as species are lost, so are their
interactions \citep{dunn2009sixth, barnosky2011has}. A community's
ability to resist collapse will depend on the community's robustness to species and interaction loss \citep{Memmott2004, Rezende2007, Bascompte2009,
  Thebault2010}. Furthermore, it has been show that biodiversity has a pivotal role in maintaining ecosystems services \citep{cardinale-2012-59}. Thus, to safeguard ecological function, it has become
increasingly imperative to aid the recovery of lost interactions and
component biodiversity and by facilitating the assembly of robust
interaction networks via ecological restoration
\citep{menz-2010-4}. However, we know very little about how ecological
networks assemble in general, rendering restoration of interacting
communities quite difficult.

@@
